BugTracking: A tool to assist in the identification of bug reports

### 2016-03-07 OSS_2016/paper.tex
Some changes in the text according to the reviewers' suggestions

\title*{BugTracking: A tool to assist in the identification of bug reports}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona\inst{1} \and Gregorio Robles\inst{1}}
%\and Name of Author\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{\texttt{gerope@libresoft.es},\texttt{jgb@gsyc.es},\texttt{grex@gsyc.es}
\and GSyC/LibreSoft, Universidad Rey Juan Carlos}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

The tool works in a browser, displaying the main characteristics to distinguish bug report from others issues. Developers will be responsible to classify the issues from Launchpad, as bug report or not, and can thereby explain their decision for each issue. We will refer issue as ticket in this paper.
(FIXME: The concept of a "ticket" should explaind first time it is mentioned (section 2))

@@

This tool works with Launchpad as issue-tracking system and Gerrit as code review system. The image \ref{fig:1} presents the architecture used, which has been developed with JavaScript, Node, JQuery and HTML5 technologies. The server side works making queries to the API of Gerrit an Launchpad, and the client side is where the user can see the information displayed, and interacts with the server through events. Both sides share the information required using JSON files and use their own REST API. Furthermore, to integrate some functionalities from GitHub, we use a third-party application between GitHub and the browser. (FIXME: it is a bit misleading to write that "image 1 presents the architecture used, which has been developed with JavaScript, Node, JQuery and HTML5 technologies.". It is probably not the architecture that has been developed using these technologies, but rather the software is based on the architecture presented in Figure 1.)

@@

The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its corresponding review in Gerrit. (FIXME: The two subsequent sentences are very strange and hard to understand, should really be rephrased for clarity.)Some information displayed link with the original web pages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done. Could tracking the history since the ticket opens until the commit fixed the ticket. ( Is this way better? The developer can access to the Launchapd and Gerrit web pages through the links displayed in tool, thereby the developers can have extra information such as the comments that other developers have done in Launchpad or gerrit. This way, they could track the history of the ticket since it was open until the fix commit closed it. )

@@

The web page provides different functionalities depending on in which tab we are. Next we explain these functionalities.
\begin{enumerate}
  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze. Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon.
  \item Tab Analyze: Is the Tab showed in Figure \ref{fig:2} where the user selects/inserts an identifier of a ticket and analyze with all the data displayed if the ticket is a bug report or not.
  \item Tab Statistics: (FIXME: Language needs to be improved in remainder of this para.)This tab collects the data saved in the user's repository in GitHub after analyzing each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
  \item Tab Modify: In this tab, the user can see all his data saved in the GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
\end{enumerate}

We continue developing the tool but an initial version is available\footnote{\url{bugtracking.libresoft.es}}, as well as a demonstration video\footnote{\url{https://www.youtube.com/watch?v=q0-TIvL4mqc&feature=youtu.be}}. It presents a license type GPL 0 (General Public License) and you can find the code at a GitHub page\footnote{\url{https://github.com/Gemarodri/BugTracking}}. Anyone can use it regardless of having GitHub account or not. (FIXME: Language needs to be improved in remainder of this para.) But, the ones with GitHub account are the only ones that can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack which you want to analyze.

@@

\section{Results}
\label{sec:4}
(FIXME: (Review)The test of the tool in section 3 involves three developers use of the tool in order to identify which issues are perceived as bug reports. My concern (or observation) is that it is not obvious that the results primarily are connected to the tool (but rather use of the tool), i.e. it could be claimed that the actual object(s) of study are the developers and how similarly the perceive issues being bug reports. What would the results look like if the tool was not used (but rather the data sources in isolation) or some other possible tool? I am not saying that the test/investigation is without value, but I think this should be discussed somewhere in the paper.
)
We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 from Nova, 125 from Horizon and 84 from Neutron. Table ~\ref{tab:1} shows the percentage of issues classified as bug reports for the different developers,  (FIXME: Discuss (more clearly) why results are not reported in Table 2 for combinations "D1 and D3" for Nova, "D2 and D3" for Horizon, and "D1 and D2" \& "D2 and D3" for Neutron.)
\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

@@

%The next step in the tool is implement the part in where we analyzed the previous commit, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
(FIXME: This section needs to be linguistically improved)
Future extensions of this tool includes extract information from others systems as Bugzilla or GitHub and study the misclassification in this projects. Also, display to users more information such as the status of the files affected in the fix commit after and before the bug-introducing. Furthermore, we would like to implement an auto classifier based on the semantic of the issue description and fix-commit description to help developers, showing a first idea about whereas the issue belongs to bug report or not, but the developer always has the last decision. After manually analyzing more than 400 tickets, we have seen clear cases of issues that were bug reports, which have similar sentences in the description, so the automatic classification will allow developers to focus only on problematic issues, which can be easily misclassified. \\
(FIXME: it is understood that the current version of the tool is limited to Openstack projects/services and with the server operating against Launchpad and Gerrit. How well can the tool support other OSS projects through use of other kinds of repositories. This is hinted in 3.1 )\\
(FIXME: There are three styles specifying authors in the reference list. Make it uniform and conformant with the Springer conference paper requirements. Do not use "et al." in reference list, list all authors. For references 1 and 2 the source is not specified.
)
\input{referenc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\title*{BugTracking: A tool to assist in the identification of bug reports}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Gema Rodr\'iguez-P\'erez\inst{1}, Jes\'us M. Gonzalez-Barahona\inst{2}, Gregorio Robles\inst{2},Dorealda Dalipaj\inst{1} \and Nelson Sekitoleko\inst{1}}
%\and Name of Author\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{\texttt{\{gerope,ddalipaj,snelson}\}@libresoft.es, LibreSoft, University King Juan Carlos
\and \texttt{\{jgb,grex\}}@gsyc.es, GSyC, University King Juan Carlos}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

The tool works in a browser, displaying the main characteristics to distinguish bug report from others issues. Developers will be responsible to classify the issues from Launchpad, as bug report or not, and can thereby explain their decision for each issue. That issues is what will refer through this paper as ticket.

@@

This tool works with Launchpad as issue-tracking system and Gerrit as code review system. The figure \ref{fig:1} presents the architecture used in the software, which has been developed with JavaScript, Node, JQuery and HTML5 technologies. The server side works making queries to the API of Gerrit an Launchpad, and the client side is where the user can see the information displayed, and interacts with the server through events. Both sides share the information required using JSON files and use their own REST API. Furthermore, to integrate some functionalities from GitHub, we use a third-party application between GitHub and the browser. (FIXME: it is a bit misleading to write that "image 1 presents the architecture used, which has been developed with JavaScript, Node, JQuery and HTML5 technologies.". It is probably not the architecture that has been developed using these technologies, but rather the software is based on the architecture presented in Figure 1.)

@@

The left side in the figure \ref{fig:2}, shows the information related with the ticket in Launchpad and its corresponding review in Gerrit. (FIXME: The two subsequent sentences are very strange and hard to understand, should really be rephrased for clarity.)Some information displayed link with the original web pages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done. Could tracking the history since the ticket opens until the commit fixed the ticket. ( Is this way better? The developer can access to the Launchapd and Gerrit web pages through the links displayed in tool, thereby the developers can have extra information such as the comments that other developers have done in Launchpad or gerrit. This way, they could track the history of the ticket since it was open until the fix commit closed it. )

@@

The web page provides different functionalities depending on in which tab we are. Next we explain these functionalities.
\begin{enumerate}
  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze. Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon.
  \item Tab Analyze: Is the Tab showed in Figure \ref{fig:2} where the user selects/inserts an identifier of a ticket and analyze with all the data displayed if the ticket is a bug report or not.
  \item Tab Statistics: This tab extracts the data already, analyzed by each developer involved in the analysis, from their users' accounts in GitHub. It analyzes this data to display a table with the number of tickets classified into the three categories; \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided}. To display the statistics of a developer, previously the name of developer has to be selected.
  \item Tab Modify: In this tab, the user can see the data saved in his GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
\end{enumerate}

We continue developing the tool but an initial version is available\footnote{\url{bugtracking.libresoft.es}}, as well as a demonstration video\footnote{\url{https://www.youtube.com/watch?v=q0-TIvL4mqc&feature=youtu.be}}. It presents a license type GPL 0 (General Public License) and you can find the code at a GitHub page\footnote{\url{https://github.com/Gemarodri/BugTracking}}. Anyone can use it regardless of having GitHub account or not. (FIXME: Language needs to be improved in remainder of this para.) But, only the ones with GitHub account can use the GitHub available functionalities; saved the data analyzed, see the statistics and modified the data saved. The one requirement is open a repository in GitHub with the same name that the project you want to analyze in OpenStack.

@@

\section{Results}
\label{sec:4}
(FIXME: (Review)The test of the tool in section 3 involves three developers use of the tool in order to identify which issues are perceived as bug reports. My concern (or observation) is that it is not obvious that the results primarily are connected to the tool (but rather use of the tool), i.e. it could be claimed that the actual object(s) of study are the developers and how similarly the perceive issues being bug reports. What would the results look like if the tool was not used (but rather the data sources in isolation) or some other possible tool? I am not saying that the test/investigation is without value, but I think this should be discussed somewhere in the paper.
)
We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 from Nova, 125 from Horizon and 84 from Neutron. All the tickets have been analyzed by two of the three developers and the Table ~\ref{tab:1} shows the percentage of tickets classified as bug reports for the different developers. These results don't report for some combinations of developers because of  in some projects, only a developer analyzed all the tickets and the two remaining analyzed the half of these tickets each one.   (FIXME: Discuss (more clearly) why results are not reported in Table 2 for combinations "D1 and D3" for Nova, "D2 and D3" for Horizon, and "D1 and D2" \& "D2 and D3" for Neutron.)
\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

@@

%The next step in the tool is implement the part in where we analyzed the previous commit, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
(FIXME: This section needs to be linguistically improved)
The current tool is limited to OpenStack projects due to we are carrying out an empirical study which based on these data, but future extensions of this tool includes extract issues from others systems as Bugzilla or GitHub to study the misclassification in the OSS projects which use these systems. Also, display to users more information such as the code of the files affected in the fix commit, and the code in the bug seeding moment. Furthermore, we would like to implement an auto classifier based on the semantic of the ticket description and fix-commit description to help developers in the analysis. This classifier will show a percentage of confident about whereas the ticket belongs to bug report or not, but the developer always has the last decision. After manually analyzing more than 400 tickets, we have seen clear cases of issues that were bug reports, which have similar sentences in the description, so the automatic classification will allow developers to focus only on problematic issues, which can be easily misclassified. \\
(FIXME: it is understood that the current version of the tool is limited to Openstack projects/services and with the server operating against Launchpad and Gerrit. How well can the tool support other OSS projects through use of other kinds of repositories. This is hinted in 3.1 )\\
(FIXME: There are three styles specifying authors in the reference list. Make it uniform and conformant with the Springer conference paper requirements. Do not use "et al." in reference list, list all authors. For references 1 and 2 the source is not specified.
)
\input{referenc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
